%-------------------------
% Resume in Latex
% Author : Qihao He
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{datetime}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Qihao He}} & Email: \href{mailto:qi.he@maine.edu}{qi.he@maine.edu}\\
  & Work: 2075812247, Mobile: 2075709742\\
  & Address: 21 Centre Dr, Apt 8i, Orono, ME, 04469, USA\\
  & Linkedin: https://www.linkedin.com/in/qihao-he-b37412b9/
  \end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maine}{Orono, ME, 04469, USA}
      {Master of Science in Computer Engineering;  GPA: 3.5}{2014.09 -- 2018.05}

    \resumeSubheading
      {Shenzhen University}{Shenzhen, Guangdong, 518000, China}
      {Bachelor of Engineering in Electrical and Electronics;  GPA: 3.1}{2010.09 -- 2014.05}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Coding}
      {C (Intermediate), Python (Intermediate), Java (Intermediate), MATLAB (Intermediate)}
    \resumeSubItem{Skills}
      {Git, Shell/scripting, Linux Performance counter, MATLAB, Altera Quartus, Visual Studio Code, Atom, LaTeX}
    \resumeSubItem{Languages}
      {Chinese (Native), English (Full professional), Cantonese (Native), Japanese (Basic)}
    % \resumeSubItem{Other skill}
    %   {Ping Pong.}
 \resumeSubHeadingListEnd
 
 %-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
 	\resumeSubItem{Publishing in-process paper: Comparing Power and Energy Usage for Scientific Calculation with and without GPU Acceleration on a Raspberry Pi Model B+ and 3B (2018.03) ICOMP'18}
      {Explored the power and energy usage of the General-Purpose Graphics Processing Unit (GPGPU) on the Raspberry Pi and compared with them to the same calculation performed only on their CPUs. Six benchmarks were developed to do 1D \& 2D FFT with and without GPU rendering using 3 libraries.The calculation was using single precision floating point numbers.}
      
    \resumeSubItem{Published paper: Raspberry Pi 2 B+ GPU Power, Performance, and Energy Implications (2017.03, 1 Paper citation) CSCI'16}
%     {By using different benchmarks both with and without the GPU rendering and an Adafruit USB Power Gauge, the power consumption difference between GPU rendering and software rendering can be measured.}
      {Correlated graphics processing, CPU load, power consumption and total energy. By using different benchmarks both with and without the GPU rendering and an Adafruit USB Power Gauge, the power consumption difference between GPU rendering and software rendering can be measured.}

%       \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
%       \textbf{Raspberry Pi 2 B+ GPU Power, Performance, and Energy Implications} & Las Vegas, NV \\
%       \textit{\small Published paper} & \textit{\small 2017, March 20, 1 Paper citation} \\
%     \end{tabular*}\vspace{-5pt}
%     \textit{Correlated graphics processing, CPU load, power consumption and total energy. By using different benchmarks both with and without the GPU rendering and an Adafruit USB Power Gauge, the power consumption difference between GPU rendering and software rendering can be measured.}
      
      \resumeSubItem{Using Message Passing Interface (MPI) for a large-scale image processing on a Distributed-memory cluster system(2017.05)}
%       {Built benchmarks using MPI to process and filter large-scale image.}
      {Developed a benchmark that used the specific matrices to multiply each pixel of the input image and change the pixel value for filtering the input image. Used MPI for processing large-scale image.}

    \resumeSubItem{Fuzzy logic controller for a rice cooker(2015.05)}
    {The controller used MATLAB Fuzzy logic toolkit to process the cooking while maintaining the temperature in a range instead of setting a threshold. Features: Fuzzy logic preheat function, Fuzzy logic cooking process temperature controller.}
%       {The Fuzzy logic controller was built in MATLAB using the Fuzzy Logic Toolkit. Features: fuzzy logic preheat function, maintaining the cooking temperature.}

    \resumeSubItem{A simple 5-stage pipeline processor in Altera Quartus II (2014.12)}
    {The virtual processor was built from scratch and downloaded to test board. Features: calculation, memory wrote and read, and overcome data hazards.}
%       {The 5 stage pipeline processor was built from scratch using the Quartus II. Features: calculation, memory wrote and read, and overcome data hazards.}

  % \resumeSubItem{QuantSoftware Toolkit}
  %   {Open source python library for financial data analysis and machine learning for finance.}
\resumeSubHeadingListEnd
 
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
        {University of Maine}{Orono, ME, USA}
        {Volunteer Internship in the Advanced Computing Group of UMaine}{2016.01 -- 2017.12, 2018.09 -- Present}
        \resumeItemListStart
          \resumeItem{Visual wall}
            {Helped build the high-resolution 6K TV wall for scientific data demonstration, including hardware assembling, system adjusting, troubleshooting, and VNC software key-pair and tuning.}
          \resumeItem{UMaine Learn to Mod}
            {Web server front-end and back-end script building; OpenStack Virtual Machine management; Google Chrome extension development.}
        \resumeItemListEnd

%       \resumeSubheading
%         {University of Maine}{Orono, ME}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small Teaching Assistant in Electrical \& Computer Engineering} & \textit{\small 2016.01 -- 2017.12}
    \end{tabular*}\vspace{-5pt}
        \resumeItemListStart
          \resumeItem{Introduction to Programming for Engineers}
          {Taught engineers to code, debug, compile, establish connections with test boards, run scripts, build circuit schematic, IC Pinouts, and graded their homework and labs.}
          \resumeItem{Introduction to Robotics}
          {Taught and graded the lab robotics matrices calculations, coding for engineers.}
        \resumeItemListEnd  
        
    	\resumeSubheading
        {Health Equity Alliance}{Bangor, ME, USA}
        {Volunteer Internship}{2018.05 -- 2018.08}
        \resumeItemListStart
          \resumeItem{Client Information Database}
          {Rebuilt the Client Information Database using MS Office Access.}
        \resumeItemListEnd

      \resumeSubheading
        {China Great Wall Computer Shenzhen Company Limited}{Shenzhen, Guangdong, China}
        {Assembly line Worker}{2013.06 -- 2013.09}
        \resumeItemListStart
          \resumeItem{Assembled the power supply of the desktop computers product from the single board}\\
          {Necessary knowledge of the internal structure of power supply, quality control, assembly sequence, static protection, factory storage optimization, fire safety, auto quick solder, and product durability test.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Google}{Mountain View, CA}
    %   {Software Engineer}{Oct 2016 - Present}
    %   \resumeItemListStart
    %     \resumeItem{Tensorflow}
    %       {TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models.}
    %     \resumeItem{Apache Beam}
    %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
    %   \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
